---
title: "R Notebook"
output: html_notebook
---



```{r}
rm(list = ls())
```

```{r}
link='https://github.com/Bearnamedjoey/guided1/raw/main/fromPyPlus.RDS'
```

```{r}
myFile=url(link)
```


```{r}
multidata=readRDS(file = myFile)
```

```{r}
row.names(multidata)=NULL
```

```{r}
str(multidata,width = 70,strict.width='cut')
```

#hypothesis1: The overall health of a country is related to alcohol consumption, tobacco use, obesity, and Gini Index.


```{r}
hypo1=formula(Health_efa~ liters.of.pure.alcohol+Percent.of.Tobacco.Use+liters.of.pure.alcohol+Gini.Index)

```

```{r}
gauss1=glm(hypo1,
           data = multidata,
           family = 'gaussian')
```



```{r}
summary(gauss1)

```

```{r}
library(rsq)
rsq(gauss1,adj=T)

```
# Question C: The regression results indicate that health, in general, is positively 
# associated with pure alcohol consumption and tobacco usage percentage, but adversely
# associated with the Gini index. Specifically, for each additional liter of pure 
# alcohol consumed per capita, the estimated increase in overall health is 0.3859 units, 
# with all other variables held constant. Similarly, with each additional percentage 
# point of tobacco usage, the estimated increase in overall health is 0.0711 units, 
# with all other variables held constant. In contrast, for each additional unit of 
# the Gini index, the expected decrease in overall health is 0.0506 units, with 
# all other variables held constant.

# It is important to note, however, that the Gini index coefficient is not statistically
# significant, meaning that we cannot be certain that this relation is not due to 
# coincidence. Regression analysis cannot prove causality, and other factors not 
# included in the model may potentially affect overall health.


